%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\textit{Mathematics, Statistics and Computer Science Department,} Macalester College} % Job title
    {Teaching Assistant} % Organization
    {St. Paul, MN} % Location
    {Jan. 2020 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching Assistant(Preceptor) in STAT/COMP 112 Intro to the Data Science at Macalester College}
        \item {Helped students with realize multivariate visualization, data wrangling, interactivity, Leaflet, scraping data, Shinny APP, SQL, and machine learning by R(RStudio)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textit{DeWitt Wallace Library,} Macalester College} % Job title
    {Access \& Research Services Student Aide} % Organization
    {St. Paul, MN} % Location
    {Sep. 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided assistance to patrons in regards to the Integrated Library System(ILS) and gave instructions for finding materials or research guide requested}
        \item {Processed shelve and sort, check-in and check-out process of library books and materials at the circulation desk}
      \end{cvitems}
    }

%---------------------------------------------------------
   \cventry
    {Self-employed} % Job title
    {Math Tutor} % Organization
    {Jinan, China} % Location
    {Jun. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed one-to-one study programs based on high school curriculum to help students excel in learning mathematics in China}
        \item {Developed a class timing and scheduling system by Python for students having classes in record}
      \end{cvitems}
    }
    
%---------------------------------------------------------

   \cventry
    {the First BRICS Mathematics Conference} % Job title
    {Conference Member} % Organization
    {Beijing, China} % Location
    {Jul, 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Was invited to Attend and listen series of worldwide cutting-edge mathematical lectures from the conference at Chinese Academy of Sciences}
        \item {Consulted mathematicians from five BRICS countries and made a manuscript}
      \end{cvitems}
    }
    
    
\end{cventries}
