%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Final Project for Data Science course at Macalester College} % Job title
    {R for Data Science: Pizza Party} % Organization
    {} % Location
    {Oct. 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Using some data from TidyTuesday’s Pizza Party data-set, analyzed and created methods and visualizations for a pizzeria that everyone would like in New York}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Honorable Mention out of 938 teams in Mathematical Contest in Modeling} % Job title
    {Mathematical Modeling for Drone Light Show} % Organization
    {} % Location
    {Jan. 2018 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Using \textit{MATLAB}, I built models to determine the required number of drones and every drone’s initial location during the process.}
        \item {Any simple pictures or icons could be designed for the drone show by my \textit{MATLAB} program.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {\textbf{Published} in Modern Mechanical Engineering Vol.8 No.1, February, 2018} % Job title
    {Design and Optimization of Comb Drive Accelerator for High Frequency Oscillation} % Organization
    {} % Location
    {Apr. 2017 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This project is mentored by a doctor at UCLA and the final paper was published. In this work, using \textit{COMSOL} and \textit{MATLAB}, a finite element code was used for the design, optimization, and visualization of a comb drive accelerator.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {\textbf{Published} in Mathematical Study and Research Vol 19, 2017} % Job title
    {Generalizations of Locus about Fixed Point and Fixed Line Moving to Magnify and Shrink} % Organization
    {} % Location
    {Sep. 2016 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {This Chinese geometrical paper is for mathematical Olympics competitions, generalized series of problems of locus by an elegant method and visualized by \textit{Geometer Sketchpad}}
      \end{cvitems}
    }
    

\end{cventries}
